Analyzing the impact of social attributes on commit integration success

### 2017-03-15 Paper/MSRChallenge2017.tex
added a threat to validity requested by reviewers
changed a long sentence into multiple paragraphs

It is also worth noticing that in both cases the Kappa statistic increases when
adding social data (100\% and 85\% respectively) which represents a more robust
measure than \textit{correctly classified} instances, since it takes into account the
correctly guessed instances occurring by chance, and we may also notice that the
mean absolute error decreases, giving stronger confidence to our claims when
considering eventual outcomes.

@@

 Other concerns of the study include the possibility that the social factors
 have changed significantly in the past three years, the collapsing of a
 commit's build success to a single successful build and unsuccessful build
 distorted the results, and the possibility that unsuccessful builds were due to
 incorrect test cases and not low quality contributions.  Future work will be
 required to investigate the influence of these threats.

>>>>

It is also worth noting that the Kappa statistic increases in both cases when
adding social data (100\% and 85\% respectively). The Kappa statistic is a more 
robust measure than \textit{correctly classified} instances, since it takes into account the
correctly guessed instances occurring by chance. The mean absolute error also
decreases in both cases, which provides further evidences that social factors
are important when predicting build success.

@@

 Other concerns of the study include the possibility that the social factors
 have changed significantly in the past three years, the collapsing of a
 commit's build success to a single successful build and unsuccessful build
 distorted the results, and the possibility that unsuccessful builds were due to
 incorrect test cases and not low quality contributions. Also, the social factors used
 in this study may not apply to closed source applications, and the factors may
 only capture a developer's experience with open source projects. Future work 
 will be required to investigate the influence of these threats.
